PMC Survey QC Analysis

### 2021-08-19 QC_analysis.Rmd
updated QC

tres <- t(res)
head(tres)
par(mar=c(5,12,3,1))
vioplot(tres,horizontal=TRUE,las=1,xlab="mean Jaccard score")
par(mar=c(5,12,3,1))
barplot(categoryMeans,horiz=TRUE,las=1,xlim=c(0,1),xlab="mean Jaccard score")

@@

>>>>

tres <- t(res)
head(tres)

par(mar=c(5,12,3,1))
vioplot(tres,horizontal=TRUE,las=1,xlab="mean Jaccard score")
par(mar=c(5,12,3,1))
barplot(categoryMeans,horiz=TRUE,las=1,xlim=c(0,1),xlab="mean Jaccard score")

@@

# PMCs that need to be redone
tres[which(rowMeans(tres)<1),]  %>% kbl() %>% kable_paper("hover", full_width = F)
